Phenology and Mycorrhizae Manuscript

### 2023-03-27 manuscriptCode_phenologyAndMycorrhizae.Rmd
Adding the rest of the files before cleaning up

for(f in seq_along(funNames)){
  print(funNames[f])
  calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=funTypes[f],funName=funNames[f])
    gapFillFromERA_verticalProfiles(dataName=dataName,dataPath=dataPath,varName=varName,funName=funNames[f])
}
```

>>>>

for(f in seq_along(funNames)){
  print(funNames[f])
  calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funName=funNames[f])
    gapFillFromERA_verticalProfiles(dataName=dataName,dataPath=dataPath,varName=varName,funName=funNames[f])
}
```

##NEON Soil Moisture
```{r}
dataName="NEON_SoilMoisture"
NEON_ID='DP1.00094.001'
if(!file.exists(paste0(dataPath,"/",dataName))){
  dir.create(paste0(dataPath,"/",dataName))
}

if(downloadData){
  downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID,andStack=FALSE,includedSeq=43:47) #No 30
}

selectColumns <- c('horizontalPosition','verticalPosition','VSWCMean','VSWCFinalQF')
inFileName <- "SWS_30_minute.csv"
varName <- 'VSWCMean'

#for(f in seq_along(funNames)[2:3]){
f=1
  print(funNames[f])
  #calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funName=funNames[f])
  gapFillFromERA_verticalProfiles(dataName=dataName,dataPath=dataPath,varName=varName,funName=funNames[f])
#}
```
